Differential invariant signatures for planar Lie group transformations of images

### 2020-11-10 paper/newpaper.tex
minor

We begin by choosing the frames $\bar f_{\bar x} = 1$ and $\bar f_{\bar y}=  0$, which determine the group parameters $a = (1-c f_y)/f_x.$ and $b = -d f_y/f_x$. Direction substition then shows that $\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$.

Under a general action of $\phi \in \mathrm{PSL}(3,\R)$, $D$ is a relative invariant (that is, the value is multiplied by a certain factor under group transformations) of weight 2:
\begin{equation}
\label{eq:D}
D \mapsto (\det \phi')^2 D\circ \phi.
\end{equation}

It is also an invariant of $A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$. Note that the sign of $D$ does not change. We assume that $D>0$ (if it is negative, relatively little changes in the following derivation) and choose the frame $\bar f_{ \bar y \bar y} = 1$, so that $d = f_x/D^{1/2}.$

>>>>

We begin by choosing the frames $\bar f_{\bar x} = 1$ and $\bar f_{\bar y}=  0$, which determine the group parameters $a = (1-c f_y)/f_x.$ and $b = -d f_y/f_x$. Direction substition then shows that $\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$, which we saw earlier as an invariant of $A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$. Note that $D$ and $\bar f_{\bar y \bar y}$ have the same sign; in what follows we assume that $D>0$ (if it is negative, relatively little changes in the following derivation) and choose the frame $\bar f_{ \bar y \bar y} = 1$, so that $d = f_x/D^{1/2}.$
